Greedy Heuristics for Solving the Weighted Orthogonal Art Gallery Problem

### 2020-09-30 doc/paper.tex
update

        \subsection{An Alternative Greedy Heuristic}
        \fxnote{TODO: work in progress...} Greedy criterion:
          \begin{itemize}
          	\item prefer those guards with a smaller cost $w_i$;
          	\item If there are more guards with the smallest cost,
          	prefer one with the largest $S_{p_i}$.
          \end{itemize}
		\fxnote{TODO: work in progress...} Another approach DRAGAN:
           \begin{itemize}
			\item introduce a penalty function
          	\item introduce a term ``incorrect point''. For a point from D(P) we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
			\item let $incorrect_{total}$ be the total number of incorrect points from discretisazion $D(P)$
			\item let $w_{total}$ be the total sum of all weights among all verteces
			\item involve the penalty function in the objective function
				$$obj(s^{ps}; v)  = \sum_{i \in s^{ps} \cup \{v\}} w_i+ incorrect_{total}$$ or
				$$obj(s^{ps}; v) = \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ \frac{incorrect_{total}}{|D(P)|}$$\fxnote{moguce i skaliranje ove dvije vrijednosti?}
			\item start Greedy with empty solution
			\item in each iteration add such a guard to $s^{ps}$ for which the obj value is minimal
			\item end when $incorrect_{total}$ becomes 0
          \end{itemize}
      \subsection{An improvement of Greedy Solution}
      Local search and Large Neighborhood search \fxnote{TODO...}
      Local search (LS) technique is a basis of the LS--based metaheuristics. Let us define the structure of neighborhood. We define them over the set of guards.
      The first configuration of neighbourhood of some partial solution is operation of swapping; that means from a given partial solution $s^P$, we choose one guard from $s^P$ and then pick another guard from $V \setminus s^p$ w.r.t. value $obj(;)$.

      Another criterion for the neighbourhood's configuration ($k$-th) would be taking arbitrary $k$ guards $\{p_1,...,p_d\}$ from $s^p$, then drop them from $s^p$. Afterwords, for each $p_i$ which are dropped off, we take the guard which is the nearest by distance from $p_i$ and add them into $s^p$.

@@

    \subsection{Hybrid Greedy + CPLEX}
        CPLEX will soon or later degrade in its performance w.r.t. instance size. On the other hand, the later stage of Greedy increase the chance to worsen the final greedy solution.  So it makes sense to combine  partial solutions generated by  Greedy over interactions  and use CPLEX to make the (partial)  solution complete. Our approach consists of the following steps:
        \begin{enumerate}
        	\item Run a Greedy method up to $K$ iterations and obtain a partial solution $C$ (therefore, $|C| = K$); 
        	\item Take solution $C$ and make it complete via. CPLEX model. 
        	\begin{itemize}
        		\item CPLEX solves corresponding sub-problem which is formed by adding constraints $x_{p_i} = 1$, for all $p_i \in C$ into the existing WOAGP model;
        		\item we obtain a complete solution $C'$;
        	\end{itemize}
            \item return $f(C')$. 
        \end{enumerate}

       \noindent \textbf{Improvements of the above method.} The above method can serve as a basic iteration 
       of a more advanced techniques like ILP-LNS or CMSA. In this case, methods for destructing the solutions 
       has to be proposed.  Underlying idea could be:
       \begin{itemize}
       	    \item remove $N$ guards with the largest costs out of $C'$
       	    \item remove $N$ guards which have a higher amount of points from $D(P)$ covered by other guards, represented by the function
       	    \begin{align}
       	       ratio(i) = \frac{\sum_{v \in V, j \in V(i)} 1_{j \mbox{ is veasible from } v} }{|V(i)|}. 
       	    \end{align}
       \end{itemize}

>>>>

        \subsection{An Alternative Greedy Heuristic}
        \fxnote{TODO: work in progress...} Greedy criterion:
          \begin{itemize}
          	\item prefer those guards with a smaller cost $w_i$;
          	\item If there are more guards with the smallest cost,
          	prefer one with the largest $S_{p_i}$.
          \end{itemize}
		\fxnote{TODO: work in progress...} Another approach DRAGAN:
           \begin{itemize}
			\item introduce a penalty function
          	\item introduce a term ``incorrect point''. For a point from D(P) we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
			\item let $incorrect_{total}$ be the total number of incorrect points from discretisazion $D(P)$
			\item let $w_{total}$ be the total sum of all weights among all verteces
			\item involve the penalty function in the objective function
				$$obj(s^{ps}; v)  = \sum_{i \in s^{ps} \cup \{v\}} w_i+ incorrect_{total}$$ or
				$$obj(s^{ps}; v) = \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ \frac{incorrect_{total}}{|D(P)|}$$\fxnote{moguce i skaliranje ove dvije vrijednosti?}
			\item start Greedy with empty solution
			\item in each iteration add such a guard to $s^{ps}$ for which the obj value is minimal
			\item end when $incorrect_{total}$ becomes 0
          \end{itemize}
      Ties are broken by using  price-per-unit heuristic.
      \subsection{An improvement of Greedy Solution}
      Local search and Large Neighborhood search \fxnote{TODO...}
      Local search (LS) technique is a basis of the LS--based metaheuristics. Let us define the structure of neighborhood. We define them over the set of guards.
      The first configuration of neighborhood of some partial solution is operation of swapping; that means from a given partial solution $s^P$, we choose one guard from $s^P$ and then pick another guard from $V \setminus s^p$ w.r.t. value $obj(;)$.

      %Another criterion for the neighbourhood's configuration ($k$-th) would be taking arbitrary $k$ guards $\{p_1,...,p_d\}$ from $s^p$, then drop them from $s^p$. Afterwords, for each $p_i$ which are dropped off, we take the guard which is the nearest by distance from $p_i$ and add them into $s^p$.

@@

    \subsection{Hybrid Greedy + CPLEX}
        CPLEX will soon or later degrade in its performance w.r.t. instance size. On the other hand, the later stage of Greedy increase the chance to worsen the final greedy solution.  So it makes sense to combine  partial solutions generated by  Greedy over interactions  and use CPLEX to make the (partial)  solution complete. Our approach consists of the following steps:
        \begin{enumerate}
        	\item Run a Greedy method up to $K$ iterations and obtain a partial solution $C$ (therefore, $|C| = K$); 
        	\item Take solution $C$ and make it complete via. CPLEX model. 
        	\begin{itemize}
        		\item CPLEX solves corresponding sub-problem which is formed by adding constraints $x_{p_i} = 1$, for all $p_i \in C$ into the existing WOAGP model;
        		\item we obtain a complete solution $C'$;
        	\end{itemize}
            \item return $f(C')$. 
        \end{enumerate}
      \begin{comment}

       \noindent \textbf{Improvements of the above method.} The above method can serve as a basic iteration 
       of a more advanced techniques like ILP-LNS or CMSA. In this case, methods for destructing the solutions 
       has to be proposed.  Underlying idea could be:
       \begin{itemize}
       	    \item remove $N$ guards with the largest costs out of $C'$
       	    \item remove $N$ guards which have a higher amount of points from $D(P)$ covered by other guards, represented by the function
       	    \begin{align}
       	       ratio(i) = \frac{\sum_{v \in V\setminus{ \{i\}}, j \in V(i)} 1_{j \mbox{ is veasible from } v} }{|V(i)|}. 
       	    \end{align}
       \end{itemize}
      \end{comment}
